### 2025-11-01 README.Rmd
README

# publishTC

Why not publish the trend-cycle?
The goal of `publishTC` is to facilitate the computation of trend-cycle component:

- Using the Cascade Linear Filter (CLF) and the surrogate cut-and-normalise asymmetric filters, as done by [Statistique Canada](https://www.statcan.gc.ca/en/dai/btd/trend-cycle);

- Using the classical Henderson symmetric filter and the surrogate Musgrave asymmetric filters, as done by Australian Bureau of Statistics (Trewin 2003);

- Using a local Parametrization of the Musgrave asymmetric filters, as described in Quartier-la-Tente (2024);

- Extending the Henderson symmetric fiter and the surrogate Musgrave asymmetric filters to take into account additive outliers and level shifts, as described in Quartier-la-Tente (2025).

# Bibliography

Dagum, E. B., & Luati, A. (2008). A Cascade Linear Filter to Reduce Revisions and False Turning Points for Real Time Trend-Cycle Estimation. *Econometric Reviews* 28 (1-3): 40‑59. <https://doi.org/10.1080/07474930802387837>

Henderson, R. (1916). Note on graduation by adjusted average. *Transactions of the actuarial society of America* 17: 43‑48.

Musgrave, J. (1964). A set of end weights to end all end weights. *US Census Bureau [custodian]*.

Trewin, D. (2003). A guide to interpreting time series - Monitoring trends. *Australian Bureau of Statistics Information Paper*. <https://www.abs.gov.au/AUSSTATS/abs@.nsf/Lookup/1349.0Main+Features12003?OpenDocument>.

Quartier-la-Tente, A. (2024). Improving Real-Time Trend Estimates Using Local Parametrization of Polynomial Regression Filters. *Journal of Official Statistics, 40*(4), 685-715. <https://doi.org/10.1177/0282423X241283207>.

Quartier-la-Tente, A. (2025). Estimation de la tendance-cycle avec des méthodes robustes aux points atypiques. <https://github.com/AQLT/robustMA>.

>>>>

### Résumé {-}

Il est commun de désaisonnaliser des séries économiques pour étudier la conjoncture et déterminer l'état du cycle dans lequel se trouve l'économie.
Toutefois, lorsqu'elles sont trop bruitées, un lissage supplémentaire est nécessaire pour supprimer l'irrégulier et extraire la tendance de court terme, appelée tendance-cycle, qui combine la tendance de long terme et les fluctuations cycliques de court terme.
Cet article décrit l'intérêt de publier cette composante tendance-cycle, les méthodes utilisées par Statistique Canada et l'Australian Bureau of Statistic (les deux seuls instituts à publier cette composante) ainsi que deux extensions permettant de réduire le biais des estimations en temps réel et de prendre directement en compte l'impact de points atypiques afin d'éviter qu'ils ne biaisent l'estimation.
Cet article détaille également des recommandations de présentation de cette composante et comment facilement mettre en production son estimation grâce à des rapports automatisés.
Ces derniers sont appliqués à une dizaine de publications de l'Insee (environ 80 séries).

Cette étude est accompagné d'un *package* R, `publishTC`, permettant de facilement mettre en œuvre toutes les méthodes et recommandations.
Elle est également entièrement reproductible et tous les codes utilisés sont disponibles sous <https://github.com/AQLT/publishTC.wp>.

Mots clés : séries temporelles, tendance-cycle, désaisonnalisation, points de retournement.

### Abstract {-}

It is common practice to seasonally adjust economic series in order to study business outlook and determine the state of the cycle at which the economy stands.
However, when they are too noisy, additional smoothing is required to remove the irregularity and extract the short-term trend, known as the trend-cycle, which combines the long-term trend and short-term cyclical fluctuations.
This article describes the advantages of publishing this trend-cycle component, the methods used by Statistics Canada and the Australian Bureau of Statistics (the only two institutes to publish this component) as well as two extensions that reduce the bias of real-time estimates and take direct account of the impact of atypical points to prevent them from biasing estimates.
This article also describes recommendations for the presentation of this component and how to put it into production using automated reports.
These, by applying it to a dozen INSEE publications (around 80 series).

This study is accompanied by an R package, `publishTC`, making it easy to implement all the methods and recommendations.
It is fully reproducible and all the codes used are available under <https://github.com/AQLT/publishTC.wp>.

Keywords: time series, trend-cycle, seasonal adjustment, turning points.
